Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
Updated quarto file
Added additional information in the results section

>>>>

One should note that @fig-daysclosed differs slightly from Jack and Oster's [@Jack_Oster_2023] with regards to the values for Europe and Central Asia, and East Asia and Pacific. Upon further analysis, we found that, unlike in our analysis, Jack and Oster omit the data from Taiwan when generating their figure, hence why their value for East Asia and Pacific, 342, differs from our value of 334. They do not cite a reason for this in their paper, however, hence why we have decided to keep in as part of our analysis to gain a more thorough picture given the data at our disposal. As for the slight variance between our calculated value for Europe and Central Asia and Jack and Oster's, 308 and 309 respectively, we found that this disparity could not be attributed to any one particular reason. When examining the raw data directly, we found that the value calculated for the average number of days closed for nations in Europe and Central Asia agreed with our value of 308, and thus the reason for the disparity is unclear.
